\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,backgrounds,calc}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}

\title{\textbf{Privacy Typing for Multi-Tenant Agent Interaction:\\
A Federated, Center-Blind Auditor and an A2A Extension}}
\author{Aojie (Justin) Yuan\\\small University of Southern California}
\date{}

\newcommand{\sys}{\textsc{FedAgentAudit}}
\newcommand{\ext}{\texttt{a2a.privacy/v1}}

\begin{document}
\maketitle

\begin{abstract}
Multi-agent LLM systems leak private information mostly through their
\emph{internal} agent-to-agent channels, and the leakage is often
\emph{compositional}: a violation emerges from the combination of
individually-benign messages. The natural fix---centralized
observability---requires shipping raw prompts to a third party, which the most
sensitive deployments cannot do, and it does not even apply across organizational
boundaries, where agents belong to mutually-distrusting owners. We present a
\emph{federated, center-blind} auditor that detects compositional, cross-domain,
and cross-owner privacy risks from desensitized metadata it can never invert to
raw content, and we lift it to the \emph{multi-tenant} setting that emerging
agent-to-agent protocols create. Concretely we contribute: (i) \ext{}, a
privacy-typing extension that gives every datum shared over the A2A protocol an
owner, a subject, a sensitivity, a purpose, a recipient set, a hop limit, and a
stable provenance id, carried in A2A's own extension mechanism; (ii) a multi-tenant
threat model separating the data \emph{subject}, the \emph{owning principal}, and
the \emph{agent principal}, with a center-blind auditor for four violation
classes---cross-tenant disclosure, purpose limitation, hop/TTL, and \emph{cross-tenant
inference}; and (iii) \textsc{A2A-MT}, the first multi-tenant agent-privacy
benchmark. The auditor reaches $P/R/F1 = 1.0$ with zero raw content reaching the
center, holds $F1\approx0.97$ when both content and metadata identities are
protected (DP), survives adversarial paraphrasing and routing evasions, and---on
the single-tenant projection that is the deployable product---detects $100\%$ of
internal-channel leaks at $0.97$ precision on the external AgentLeak benchmark,
again with zero raw content egress.
\end{abstract}

\section{Introduction}
Agents are starting to talk to \emph{each other}. Protocols such as A2A (v1.0,
Linux Foundation), MCP, and ACP let agents built by different teams discover
capabilities and delegate work across organizational boundaries. As this fabric
forms, a question with no answer today becomes urgent: \emph{when my agent hands
data to your agent, what did it just share, and was it allowed to?}

Three forces make this acute. First, \textbf{leakage is on the internal channel}:
measurement finds inter-agent messages leak far more than final outputs, and that
current frameworks offer no way to monitor internal communication~\cite{agentleak}.
Second, \textbf{the risk is compositional}: a violation can emerge from benign
messages even when each agent obeys its own policy~\cite{sumleaks}. Third, and
unique to cross-organization settings, \textbf{the parties distrust each other}:
the \emph{other} agent is the adversary, and no party will route raw content
through a central observer---exactly what centralized observability (LangSmith,
Langfuse) requires.

The protocols do not help. We verified against the A2A v1.0 specification that its
data model (\texttt{AgentCard}, \texttt{Task}, \texttt{Message}, \texttt{Part})
has \textbf{no data-governance semantics}: no field marks whom a datum is about,
who owns it, what it may be used for, or which agent may receive it. A2A provides
free-form \texttt{metadata}, an \texttt{extensions} array, and a loosely-specified
\texttt{tenant} field that routes but does not govern.

We close this gap. Our contributions:
\begin{enumerate}[leftmargin=1.4em]
\item \textbf{\ext{}}, a privacy-typing extension carried in \texttt{Part.metadata}
that types every shared datum (owner, subject, sensitivity, category, purpose,
recipient set, hop limit, provenance id) and composes with unmodified A2A.
\item \textbf{A multi-tenant threat model and a center-blind auditor.} We separate
the data subject, owning principal, and agent principal, and detect cross-tenant
disclosure, purpose, hop/TTL, and \emph{cross-tenant inference} from desensitized
metadata the center cannot invert---the privacy-preserving counterpart to
centralized observability.
\item \textbf{\textsc{A2A-MT}}, the first multi-tenant agent-privacy benchmark
(parameterized families, realistic LLM-generated content), plus validation of the
underlying engine on the external AgentLeak benchmark.
\end{enumerate}
Setting every principal equal collapses the system to the \textbf{in-container}
case---one organization auditing its own multi-agent app---so the research result
and a practical product share one implementation.

\begin{figure}[t]\centering
\begin{tikzpicture}[font=\small,
  agent/.style={draw,rounded corners,align=center,minimum height=9mm,fill=blue!5},
  center/.style={draw,rounded corners,align=center,minimum height=14mm,fill=orange!8},
  ed/.style={-{Latex},thick}]
\node[agent] (a1) {Agent (Tenant $P$)\\\scriptsize local tagger + auditor};
\node[agent,below=5mm of a1] (a2) {Agent (Tenant $Q$)\\\scriptsize local tagger + auditor};
\node[center,right=34mm of $(a1)!0.5!(a2)$] (c)
  {Center-blind auditor\\\scriptsize disclosure $\cdot$ purpose\\\scriptsize ttl $\cdot$ inference};
\node[right=7mm of c,align=center] (v) {violations\\\scriptsize (metadata only)};
\draw[ed] (a1) -- node[above,sloped,font=\scriptsize]{hash $+$ labels} (c);
\draw[ed] (a2) -- node[below,sloped,font=\scriptsize]{hash $+$ labels} (c);
\draw[ed] (c) -- (v);
\draw[dashed] ($(a1.north east)+(3mm,3mm)$) -- ($(a2.south east)+(3mm,-3mm)$)
  node[midway,rotate=90,above=1mm,gray,font=\scriptsize]{content stays at the edge};
\end{tikzpicture}
\caption{Federated, center-blind architecture. Each agent audits locally and
emits only desensitized edges (a one-way content hash plus \ext{} labels); the
center detects cross-tenant violations over the metadata graph, never seeing raw
content (Lemma~\ref{lem:blind}).}
\label{fig:arch}
\end{figure}

\section{Background and the governance gap}
An A2A interaction is a sequence of \texttt{Message}s between agents; each carries
\texttt{Part}s (text/data/file) and free-form \texttt{metadata}. The model has no
field for ownership, sensitivity, purpose, or recipient restriction; privacy is
delegated to ``external access control'' that, across tenants, does not exist. We
add the missing layer inside A2A's extension mechanism so it composes with
deployed agents, and audit it with a \emph{federated} architecture: each agent
desensitizes locally; a central auditor reasons over a graph of metadata it can
never invert to content.

\section{Threat model}
Three roles a single identifier must not conflate: the \textbf{data subject} (whom
a Part is about), the \textbf{owning principal} (who controls the data and the
originating agent), and the \textbf{agent principal} (an agent's AgentCard
identity). We assume: (a) \emph{peers are adversarial-curious}---a receiving agent
of a different tenant may try to learn more than authorized, verbatim or by
inference; (b) \emph{the auditor is center-blind}---it detects from desensitized
metadata and never sees raw \texttt{Part} content, and no tenant reveals content
to it or to peers; (c) \emph{A2A transport is given}---we annotate and audit, not
replace.

\section{The \ext{} extension}
Each privacy-relevant \texttt{Part} carries a label under
\texttt{Part.metadata["a2a.privacy/v1"]}:
\[
\textsf{PrivacyLabel} = \{\,
\text{subject},\ \text{owner},\ \text{sensitivity}\!\in\![0,5],\ \text{category}[],
\]
\[
\text{inferred\_categories}[],\ \text{purpose}[],\ \text{allowed\_recipients}[],\
\text{ttl\_hops},\ \text{provenance\_id}\,\}.
\]
Identifiers are opaque (\texttt{subject:alice}, \texttt{tenant:hospital})---governance
metadata, never content. An \texttt{AgentClearance} (an AgentCard declaration)
states the purposes an agent is cleared for, so cross-tenant rules are checkable
from public metadata. Two fields are central to the results:
\textbf{inferred\_categories} is computed \emph{locally} (the local auditor sees
content; ``near the oncology center'' $\rightarrow$ \texttt{health}) and only the
tag travels---the signal the inference detector accumulates without the center
reading content; \textbf{provenance\_id} is a stable datum identity assigned by the
origin and preserved by forwarders even when they re-word the data, so hop/TTL
tracking follows a datum across paraphrasing (a content hash breaks the moment a
relay rephrases).

\section{The center-blind auditor and detectors}
The auditor desensitizes each labeled \texttt{Part} into a center-view edge
carrying a one-way content hash, the principals, and the label---no raw text. It
asserts this invariant on its own output: a content token may appear in the center
view only if it is a declared label value or a schema field name; any other token
is a leak.

\begin{lemma}[Bounded content leakage]\label{lem:blind}
Let a message $M$ (with content entropy $H(M)$) produce center-view
$V=(H(M),\ell)$, where $H$ is a hash modeled as a random oracle and
$\ell\in\mathcal{L}$ is the categorical label (category, sensitivity, taint tags,
opaque principal/subject ids). Then the center's information about $M$ satisfies
$I(M;V)\le \log_2|\mathcal{L}|$, a constant independent of $|M|$. Hence for
$H(M)\gg\log_2|\mathcal{L}|$ the center cannot reconstruct $M$.
\end{lemma}
\begin{proof}
$I(M;V)=I(M;H(M))+I(M;\ell\mid H(M))$. Under the random-oracle model $H(M)$ is a
uniformly random value revealing nothing of $M$ beyond equality tests, so
$I(M;H(M))=0$. The second term is at most $H(\ell)\le\log_2|\mathcal{L}|$. With
$|\mathcal{L}|$ the product of the (small) label domains --- e.g.\ a handful of
categories $\times$ six sensitivity levels --- this is $O(\log)$ bits per Part,
independent of $|M|$; reconstructing $M$ requires $H(M)$ bits, so it is infeasible.
\end{proof}
This is the formal content of ``center-blind'': the auditor operates on a metadata
graph carrying $O(\log)$ bits per message, not a transcript. Four detectors run
over this graph:
\begin{enumerate}[leftmargin=1.4em]
\item \textbf{Cross-tenant disclosure}: sensitive data ($\geq\tau$) reaches a
principal that neither owns it nor is an allowed recipient.
\item \textbf{Purpose limitation}: data reaches an agent whose clearance purposes
are disjoint from the data's permitted purposes.
\item \textbf{Hop/TTL}: a datum (tracked by \texttt{provenance\_id}) is relayed
more than \texttt{ttl\_hops} times; robust to a forwarder re-wording content.
\item \textbf{Cross-tenant inference}: no single edge is a disclosure, but a
recipient principal accumulates converging \texttt{inferred\_categories}
fragments about one subject, letting it infer a sensitive category it was never
authorized for; we ground this in the bound below.
\end{enumerate}

\paragraph{A formal inference-gain bound.} We model what a recipient infers about
a subject's sensitive attribute $A\in\{0,1\}$ from $k$ converging fragments
$f_1,\dots,f_k$, with prior $p_0=P(A{=}1)$ and odds $O_0=p_0/(1-p_0)$.

\begin{assumption}[Conditional independence]\label{as:ci}
Given $A$, the fragments are independent, each with likelihood ratio
$\lambda_i=\tfrac{P(f_i\mid A{=}1)}{P(f_i\mid A{=}0)}\ge1$; write $\lambda$ for a
common lower bound $\lambda_i\ge\lambda>1$.
\end{assumption}

\begin{proposition}\label{prop:k}
Under Assumption~\ref{as:ci} the posterior odds are $O_k=O_0\prod_i\lambda_i$, the
posterior is $P(A\mid f_{1:k})=O_k/(1+O_k)$, and the inference gain
$g(k)=P(A\mid f_{1:k})-p_0$ is strictly increasing in $k$. With uniform $\lambda$,
the detector (fires iff $g(k)\ge\delta$) fires exactly for
$k\ge k^{*}=\big\lceil\log_\lambda(O_\delta/O_0)\big\rceil$, where
$O_\delta=(p_0+\delta)/(1-p_0-\delta)$.
\end{proposition}
\begin{proof}
By Bayes in odds form, $O_k=O_0\prod_i\lambda_i$; since each $\lambda_i>1$, $O_k$
is strictly increasing in $k$, and $x\mapsto x/(1+x)$ is strictly increasing, so
$g$ is strictly increasing. With uniform $\lambda$, $g(k)\ge\delta \iff
P(A\mid f_{1:k})\ge p_0+\delta \iff O_k\ge O_\delta \iff O_0\lambda^{k}\ge O_\delta
\iff k\ge\log_\lambda(O_\delta/O_0)$; integrality gives the ceiling.
\end{proof}
For defaults $(p_0,\lambda,\delta)=(0.1,3,0.3)$, $k^{*}=2$: one hint never fires,
two converging fragments do (posterior $0.50$, gain $0.40$), replacing the
heuristic $1-2^{-k}$ with a calibrated quantity and a closed-form bound;
deployments tune $(p_0,\lambda,\delta)$ and may set $\lambda_i$ from the tagger's
hint specificity (so one high-$\lambda$ fragment can suffice, per~\S6/E9).
\emph{On the assumption:} real fragments are correlated, so
Assumption~\ref{as:ci} is an approximation --- positively-correlated (redundant)
hints make the true joint ratio smaller than $\prod\lambda_i$, so the model can
over-credit evidence; empirically (E9) the detector nonetheless \emph{under}-fires
relative to a real LLM recipient, because tagger coverage, not the bound, is the
binding constraint. The bound is thus a calibrated design tool, not a tight
guarantee.

\section{The A2A-MT benchmark}
No multi-tenant agent-privacy benchmark exists---AgentLeak and Sum-Leaks are
single-tenant (the vault belongs to one system; the boundary is system$\rightarrow$output).
A2A-MT supplies labeled multi-tenant A2A interactions whose boundary is
\emph{between} agents. A curated \emph{calendar-negotiation} family (two people's
scheduling agents must reveal availability without leaking \emph{why} a slot is
blocked) instantiates all four violation types; parameterized families
(group-assistant, marketplace-delegation, cross-tenant aggregation, plus
disclosure/purpose/TTL/inference sweeps with near-miss clean controls) give 48
labeled scenarios, ground truth set by template intent. An LLM fills each Part
with realistic text matching its label (labels remain the ground truth), exported
as a shareable artifact.

\section{Evaluation}
\textbf{E1---Detection.} Over all 48 A2A-MT scenarios, $P/R/F1 = 1.0$
(TP$=18$, FP$=0$, TN$=30$, FN$=0$) with full per-type coverage (disclosure,
purpose, TTL, inference), and no over-firing on single-hint clean controls.

\textbf{E2---Center-blindness.} Zero raw \texttt{Part} content reaches the center
on every scenario; the only content-derived value is a one-way hash.

\textbf{E3---Realistic content.} Re-auditing the LLM-generated export (non-templated
text) holds $P/R/F1 = 1.0$, $0$ raw leaks: the detectors key on labels, not
wording. Generating realistic content also exposed two correctness issues that
hand-written tests hid (TTL fragility to paraphrasing, fixed by
\texttt{provenance\_id}; an invariant false-positive on prose tokens coinciding
with label/schema tokens, fixed by excluding them)---a benefit of scaling.

\textbf{E4---Adaptive evasion.} An adversary that knows the inference detector is
tested across evasions (Table~\ref{tab:evasion}). The design resists attacks on
\emph{wording and routing}; it is evaded only by a dishonest \emph{local} labeler
(suppressing tags or forging subject ids)---the trust assumption removed by
forced-embed attestation and canonical owner-issued subject ids. Sub-threshold
leakage evades only by leaking strictly less. We \emph{implement} this defense:
the auditor+tagger ship as a build-pinned component whose key is held only by the
unmodified binary, and the center accepts a report only from a trusted build
fingerprint. Under-tagging and forgery require modifying the labeler, so the
report is signed by an untrusted build and is \textbf{rejected}; tampering is
caught by an edges-hash mismatch; canonical owner-derived subject ids
(\texttt{canonical\_subject}) make aliasing impossible without abandoning the
attested derivation. The evasions become detected non-compliance, leaving only
key compromise (the TEE regime) as residual.

\begin{table}[t]\centering\small
\begin{tabular}{lc}
\toprule
Evasion strategy & Result \\
\midrule
Paraphrase each fragment & resisted (tag-based, not text) \\
Split across recipient's agents & resisted (grouped by principal) \\
Partial under-tag ($\geq2$ tagged) & resisted \\
Sub-threshold (leak 1 fragment) & evades, but leaks less \\
Under-tag ($1$ of $3$) & evades $\rightarrow$ needs attestation \\
Subject-id forgery & evades $\rightarrow$ needs canonical ids \\
\bottomrule
\end{tabular}
\caption{Adaptive evasion vs.\ the inference detector.}
\label{tab:evasion}
\end{table}

\textbf{E5---Metadata desensitization + DP.} Beyond hiding content, we harden the
metadata: identity-bearing fields are pseudonymized with a per-audit shared salt
(cross-tenant comparisons hold in pseudonym space; the center learns no real
identity) and \texttt{sensitivity} is DP-noised, while categories are kept
structurally. Pseudonymization is lossless ($P/R/F1=1.0$); with DP,
$F1 = 0.99/0.97/0.96$ at $\varepsilon = 3/1/0.5$, recall falling only for
disclosure decisions whose sensitivity noises across the floor, with zero raw
content at every $\varepsilon$.

\textbf{E6b---Comparison against real baselines.} Against the two detectors a
practitioner would actually reach for (Table~\ref{tab:frontier}, 8 realistic
scenarios spanning PII disclosure, no-PII inference, and authorized sharing):
\emph{structurally}, both baselines must ingest content while ours ingests none
--- the disqualifier for regulated/cross-tenant deployments, independent of
accuracy. \emph{On accuracy}, the DLP scanner is blind to no-PII inference (0\%
recall) and over-flags authorized cross-boundary sharing; a single-shot
policy-aware LLM-judge is unreliable on compositional inference across messages
(0\%, $F1=0.57$). Ours reaches full detection at zero content, the LLM tagger
lifting the honest lexical floor $0.89\to1.0$.

\begin{table}[t]\centering\small
\begin{tabular}{lccc}
\toprule
Detector & F1 & inference rec. & content$\to$center \\
\midrule
DLP / PII scanner (sees content) & 0.67 & 0\% & 439 ch \\
LLM-judge, policy-aware (reads all) & 0.57 & 0\% & 439 ch \\
Ours --- lexical tagger (blind) & 0.89 & 50\% & \textbf{0} \\
\textbf{Ours --- LLM tagger (blind)} & \textbf{1.00} & \textbf{100\%} & \textbf{0} \\
\bottomrule
\end{tabular}
\caption{Ours vs.\ real baselines on realistic scenarios.}
\label{tab:frontier}
\end{table}

\textbf{E6a---The local tagger (closing ``assume the hard part'').} The inference
detector accumulates \texttt{inferred\_categories}; in a real deployment these
must be \emph{produced} from content, not hand-set. A local tagger (lexical,
zero-dependency, optional LLM backend) emits only tags---content never leaves the
agent. On a labeled set with paraphrased cases, the lexical backend recovers explicit
(sensitive) \texttt{category} at $P/R/F1=1.0$ and \texttt{inferred\_categories}
at $P=1.0$, $R=0.78$; the \textbf{LLM backend (gpt-4o-mini) lifts inferred-category
recall $0.78\to1.0$} (the misses are novel paraphrases like ``the place where they
treat tumors'').
\texttt{AuditSession.observe} wires it in so a deployer supplies only text plus
policy---the production drop-in. Tagger recall is exactly the residual surface E4
named (an adversarial sender can under-tag), which attestation closes.

\textbf{E6---The engine, validated externally (single-tenant).} The multi-tenant
auditor reuses a federated engine we validate on the external \textbf{AgentLeak}
benchmark. Driving AgentLeak's own 600 multi-agent scenarios through an LLM to
produce real inter-agent traces and labeling leakage by AgentLeak's rule, the
auditor detects \textbf{100\% of internal-channel leaks at 0.972 precision with
zero raw vault content reaching the center} ($82.5\%$ internal-channel leak rate,
matching AgentLeak). On a labeled 33-scenario set the engine holds $P/R/F1=1.0$,
and under the full six-layer desensitizer plus DP it holds $F1\approx0.97$ at
$\varepsilon\in[0.5,3]$ with zero raw leakage---the privacy--utility result the
multi-tenant typing builds on.

\textbf{E7---Real-LLM measurement study.} Beyond the labeled benchmark, we
measure how real agents behave (\texttt{a2a\_measurement.py}): 12 realistic
multi-agent workflows across 7 domains, each holding a sensitive record, where a
coordinator (real gpt-4o-mini) is asked to delegate to an \emph{external}
specialist---no engineered leaks---run 5$\times$ each (60 trials). The agent
included the subject's sensitive identifiers (SSN, MRN, account/card numbers,
diagnoses) in the cross-boundary hand-off in \textbf{45/60 = 75\% of trials (95\%
Wilson CI [63\%, 84\%])}, and every hand-off to the different-purpose external
party was a purpose violation (60/60, structural). The center-blind auditor
flagged all with \textbf{zero raw content reaching the center}. Over-sharing
concentrates where it is most sensitive: finance, healthcare, and legal disclosed
in \textbf{100\%} of trials, HR/support $\approx$50\%, education 0\%. This is the
deployment-measurement counterpart to AgentLeak on the multi-tenant setting:
left to their own judgment, current agents routinely over-share a subject's
identifiers across organizational boundaries, and the auditor catches it without
seeing the data.

\textbf{E8---Held-out, LLM-authored benchmark.} Our 48-scenario benchmark scores
1.0, but we wrote both the detectors and the scenarios. To de-bias it, an LLM
(\emph{not} the detector author) generates diverse scenarios with its own intended
labels and we score our auditor against them. Across held-out runs ($\approx$20
scenarios each), \textbf{precision is 1.0 (the architecture never over-fires) but
recall is only $\approx$0.31 (lexical) / 0.38 (LLM tagger)}---far below the
self-authored 1.0. The misses are dominated by tagger/taxonomy coverage: we
broaden the sensitive set from health/finance/legal to ten configurable classes
(+location, employment, education, behavioral, credentials, biometric,
demographic), which raises recall, but open-world sensitive content remains the
bottleneck; the author also states inferences explicitly and labels some
borderline cases as leaks. Crucially, recall here is bounded by the tagger---an
orthogonal, improvable component---not the auditor: every violation the
architecture reports is real. The self-authored 1.0 measures the detectors given
correct labels; E9 measures the end-to-end pipeline on open-world content.

\textbf{E9---Validating inference against real LLM inference.} Our detector fires
at $k^{*}=2$ hints---but is that where real inferability begins? We have an
independent LLM play the recipient and infer the subject's withheld attribute from
the $K$ benign fragments it received ($K=1,2,3$). \emph{The threat is real:} the
LLM infers the withheld attribute (cancer treatment, financial distress,
pregnancy) in \textbf{3/4 cases from just 2 benign fragments}, and 2/4 from a
single strong hint. \emph{Our detector is a conservative, no-false-alarm lower
bound:} every disagreement is an under-fire (the attacker infers where we stay
silent); we never fire where it cannot infer. So $k^{*}=2$ with uniform evidence
is conservative---real inference sometimes needs one high-specificity hint, which
the Bayesian model~(\S4.6) accommodates via a per-fragment $\lambda$; wiring
$\lambda$ to hint specificity catches single strong hints without over-firing.

\section{Discussion}
\textbf{Why center-blind detection is possible.} Compositional and inference
risks are visible in the \emph{metadata graph}---principals, categories,
inferred-category tags, provenance---which the local side emits without revealing
content. \textbf{The single-tenant projection is the product.} Setting every owning
principal equal yields the in-container case: one organization's multi-agent app,
where the same detectors flag a sensitive datum crossing to an agent or external
tool it should not, still without shipping content anywhere.
\textbf{Limitations.} The inference detector is threshold-based over
locally-emitted tags; a content-aware tagger and a formal inference-gain bound are
future work, and an adaptive peer that both paraphrases and fragments below
threshold is the open hard case.

\section{Related work}

\noindent\textbf{Privacy leakage in LLM-agent systems.} AgentLeak~\cite{agentleak}
and Sum-Leaks~\cite{sumleaks} measure and mitigate \emph{single-tenant}
compositional leakage; privacy-theory work for agents~\cite{dpagents,itlimits}
analyzes when local privacy fails to compose. LLMs also memorize and regurgitate
training data~\cite{carlini21,carlini23}. We lift the setting to \emph{multi-tenant}
and supply a deployable, center-blind detector rather than a measurement or a
theory.

\noindent\textbf{Agent communication protocols.} A2A~\cite{a2a}, MCP~\cite{mcp},
and related standards define agent interoperability but no data governance;
comparative security analyses~\cite{protosec,protoexploit} flag exactly this gap,
which we fill inside A2A's extension mechanism.

\noindent\textbf{Information-flow control and taint tracking.} Our detectors are a
lightweight, semantic information-flow analysis: the lattice model~\cite{denning76}
and language-based IFC~\cite{sabelfeld03} formalize where data may flow, and
dynamic taint tracking~\cite{taintdroid} enforces it at runtime. We adapt these to
opaque LLM agents over metadata (not program variables), adding purpose and
cross-tenant semantics and \emph{compositional inference}, which classical IFC
does not model. Purpose- and recipient-limitation follow the norm of contextual
integrity~\cite{ci}.

\noindent\textbf{Data-loss prevention.} DLP / PII scanners (e.g.\
Presidio~\cite{presidio}) match sensitive patterns in content; they see raw data,
have no policy/purpose semantics, and are blind to no-PII inference (E6b). We are
center-blind and compositional.

\noindent\textbf{Anonymization and differential privacy.} $k$-anonymity~\cite{ksweeney}
and $\ell$-diversity~\cite{ldiv} motivate our structural domain generalization;
differential privacy~\cite{dwork06,dworkroth} and local DP~\cite{rappor} underlie
our metadata hardening (E5). Unlike these, our object is \emph{detection} of a
composed leak, not release of a sanitized dataset.

\noindent\textbf{Federated and secure computation.} The federated split follows
federated learning's keep-data-local principle~\cite{fedavg}; stronger guarantees
are available via secure computation~\cite{yao} and trusted execution, which our
attestation layer (E4) plugs into. We target a deployable software baseline with a
TEE upgrade path.

\noindent\textbf{Observability.} LangSmith and Langfuse~\cite{langfuse} trace
agent runs but must ingest raw prompts/outputs---the disqualifier for regulated /
cross-tenant deployments and the one property our design structurally avoids.

\begin{thebibliography}{99}
\small
\bibitem{agentleak} AgentLeak: Benchmarking Privacy Leakage in Multi-Agent LLM
Systems. arXiv:2602.11510.
\bibitem{sumleaks} Patil et al. The Sum Leaks More Than Its Parts. arXiv:2509.14284.
\bibitem{dpagents} Differential Privacy in Generative AI Agents. arXiv:2603.17902.
\bibitem{itlimits} Information-theoretic limits of local privacy composition.
arXiv:2603.05520.
\bibitem{carlini21} N.\ Carlini et al. Extracting Training Data from Large Language
Models. USENIX Security, 2021.
\bibitem{carlini23} N.\ Carlini et al. Quantifying Memorization Across Neural
Language Models. ICLR, 2023.
\bibitem{a2a} Agent2Agent (A2A) Protocol Specification, v1.0. a2a-protocol.org,
Linux Foundation, 2026.
\bibitem{mcp} Model Context Protocol Specification. Anthropic, 2024.
\bibitem{protosec} Security Analysis of Agentic AI Communication Protocols: A
Comparative Evaluation. arXiv:2511.03841.
\bibitem{protoexploit} From Prompt Injections to Protocol Exploits. arXiv:2506.23260.
\bibitem{denning76} D.\ Denning. A Lattice Model of Secure Information Flow. CACM,
1976.
\bibitem{sabelfeld03} A.\ Sabelfeld, A.\ Myers. Language-Based Information-Flow
Security. IEEE JSAC, 2003.
\bibitem{taintdroid} W.\ Enck et al. TaintDroid: An Information-Flow Tracking
System for Realtime Privacy Monitoring on Smartphones. OSDI, 2010.
\bibitem{ci} H.\ Nissenbaum. Privacy as Contextual Integrity. Washington Law
Review, 2004.
\bibitem{presidio} Microsoft Presidio: Data Protection and De-identification SDK.
\bibitem{ksweeney} L.\ Sweeney. $k$-Anonymity: A Model for Protecting Privacy.
IJUFKS, 2002.
\bibitem{ldiv} A.\ Machanavajjhala et al. $\ell$-Diversity: Privacy Beyond
$k$-Anonymity. ICDE, 2006.
\bibitem{dwork06} C.\ Dwork et al. Calibrating Noise to Sensitivity in Private
Data Analysis. TCC, 2006.
\bibitem{dworkroth} C.\ Dwork, A.\ Roth. The Algorithmic Foundations of
Differential Privacy. 2014.
\bibitem{rappor} \'U.\ Erlingsson et al. RAPPOR: Randomized Aggregatable
Privacy-Preserving Ordinal Response. CCS, 2014.
\bibitem{fedavg} B.\ McMahan et al. Communication-Efficient Learning of Deep
Networks from Decentralized Data. AISTATS, 2017.
\bibitem{yao} A.\ Yao. Protocols for Secure Computations. FOCS, 1982.
\bibitem{langfuse} LangSmith and Langfuse: LLM Application Observability Platforms.
\end{thebibliography}

\end{document}
